---
title: "Impact Report: Accelerator 2019-21"
subtitle: "Menstrual Health and Hygiene"
author:
- name: Taylor Conger
  affiliation: Duke university, Innovation and Enterprise
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::html_clean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r load_libraries}
library(tidyverse)
library(plotly)
library(stringi)
library(scales)
library(stringr)
library(plotly)
library(textstem)
library(shiny)
library(lubridate)
library(rmdformats)

```


```{r import_data}
baseline_data <- read_csv("data/Cohort 1 M&E Analysis_Baseline_trimmed.csv", show_col_types = FALSE)
midline_data <- read_csv("data/Cohort 1 M&E Analysis_Midline_trimmed.csv", show_col_types = FALSE)
endline_data <- read_csv("data/Cohort 1 M&E Analysis_Endline_trimmed.csv", show_col_types = FALSE)
```

```{r data_clean}

baseline_data <- baseline_data %>% 
                  drop_na(OrgID) %>% 
     mutate(Organization = ifelse(str_detect(Organization, "SaCo"),"SaCoDé",Organization))

midline_data <- midline_data %>% 
                  drop_na(OrgID) %>% 
     mutate(Organization = ifelse(str_detect(Organization, "SaCo"),"SaCoDé",Organization))

endline_data <- endline_data %>% 
                  drop_na(OrgID) %>% 
                 mutate(Organization = ifelse(str_detect(Organization, "SaCo"),"SaCoDé",Organization))


```

```{r load_color_scheme, echo=FALSE}
#Page styling

#This is where you create your own custom color palette for the traces.
duke_colorway = c("#C84E00","#E89923","#FFD960","#A1B70D","#339898","#1D6363","#005587","#0577B1","#993399")

#This controls the background color for the entire chart. Probably best left white.
duke_paperbackground = c('rgba(255,255,255,0)')

#This controls the background for the plot. Probably best left white.
duke_plotcolor = c('rgba(255,255,255,.4)')

#Margin 

m <- list(l = 50, r = 50, b = 50, t = 50, pad = 4)

#Caption Style

fig_caption <- "font-family: 'Playfair Display','Helvetica Neue',Helvetica,Arial,sans-serif; font-weight: normal; font-size:110%"

plot_font <- list(
  family = "'Playfair Display','Helvetica Neue',Helvetica,Arial,sans-serif",
  size = 15,
  color = '#363636')


```


## Introduction

The following data was compiled using three separate surveys: a) an intake survey administered at the beginning of the program; b) a midline survey; c) and an end-point survey. When these surveys were devised at the beginning of the program in 2019 they could not anticipate the vicissitudes that would be wrought by the COVID-19 pandemic. Consequently, later iterations of the survey probed different points of saliency. Additionally, questions were also revised as part of on iterative process to refine the survey more generally. On occasion, this has meant that questions are not always perfectly in alignment between different measuring points. All cases of such discrepancies have been noted.


## Target Demographics

Widely ranging in their approach, the six projects were also operating in different contexts. During the initial phases of the fellowship, the target demographics skewed overwhelmingly towards lower-income rural users. Over the course of the fellowship, the target demographic shifted more towards higher-income and urban beneficiaries. 

### Economic Target Group

The organizations were surveyed on their target population.  

```{r economic_demographics}
baseline_economic_demo <- baseline_data %>%
  drop_na(OrgID) %>%
  select(Survey:lower_income) %>%
  pivot_longer(high_income:lower_income,
               names_to = "income_level",
               values_to = "Percent") %>%
  group_by(Survey,income_level) %>%
  summarise(total = round(mean(as.numeric(Percent),0))) %>% 
  mutate(income_level = str_to_title(str_replace_all(income_level,"_"," ")))
```

### Economic Plot Baseline

```{r economic_demographics_plot}

plot_economic_demographics <- baseline_economic_demo %>% 
                              plot_ly(
                              labels = ~income_level, 
                              values = ~total, 
                              type = 'pie')

plot_economic_demographics <- plot_economic_demographics %>% 
  layout(title = "Economic Target Population: Baseline",
         colorway=duke_colorway,
         paper_bgcolor = duke_paperbackground,
    plot_bgcolor = duke_plotcolor,
     margin = m,
    font=plot_font
     )

plot_economic_demographics

```


### Economic Plot Midline

```{r midline_economic_demo}
midline_economic_demo <- midline_data %>%
  drop_na(OrgID) %>%
  mutate(across(high_income:lower_income, as.integer)) %>% 
  
         select(Survey:lower_income) %>%
  
  pivot_longer(high_income:lower_income,
               names_to = "income_level",
               values_to = "Percent") %>%
  group_by(Survey,income_level) %>%
   summarise(total = round(mean(as.numeric(Percent),0))) %>% 
  mutate(income_level = str_to_title(str_replace_all(income_level,"_"," ")))
```


```{r economic_demographics_plot_midline}

plot_economic_demographics_midline <- midline_economic_demo %>% 
                              plot_ly(
                              labels = ~income_level, values = ~total, type = 'pie')

plot_economic_demographics_midline <- plot_economic_demographics_midline %>% 
  layout(title = "Economic Target Population: Midline",
         colorway=duke_colorway,
         paper_bgcolor = duke_paperbackground,
    plot_bgcolor = duke_plotcolor,
     margin = m,
    font=plot_font
     )

plot_economic_demographics_midline

```

### Economic Plot Endline

```{r endline_demographic_demo}
endline_economic_demo <- endline_data %>%
  
  mutate(across(high_income:lower_income, as.integer)) %>% 
  
         select(Survey:lower_income) %>%
  
  pivot_longer(high_income:lower_income,
               names_to = "income_level",
               values_to = "Percent") %>%
  group_by(Survey,income_level) %>%
   summarise(total = round(mean(as.numeric(Percent),0))) %>% 
  mutate(income_level = str_to_title(str_replace_all(income_level,"_"," ")))



```



```{r plot_endline_demographic_demo}
plot_economic_demographics_endline <- endline_economic_demo %>% 
                              plot_ly(
                              labels = ~income_level, values = ~total, type = 'pie')

plot_economic_demographics_endline <- plot_economic_demographics_endline %>% 
  layout(title = "Economic Target Population: Endline",
         colorway=duke_colorway,
         paper_bgcolor = duke_paperbackground,
    plot_bgcolor = duke_plotcolor,
     margin = m,
    font=plot_font
     )

plot_economic_demographics_endline
```

### Observations

There is a shift away from lower income and towards middle and higher income. Part of this shift can be explained by a slight change in the phrase of the question. i.e. Poor and Very Poor, were not part of the initial survey. Expecting that this could also be explained by....


### Alternative visualization

This is another version of the same data that is more compact and shows the most important difference.

```{r}
all_demographic_economic <- baseline_economic_demo %>%
  bind_rows(midline_economic_demo) %>%
  bind_rows(endline_economic_demo) %>%
  mutate(income_level = str_to_lower(str_replace_all(income_level, " ", "_"))) %>%
  pivot_wider(names_from = income_level, values_from = total)

all_demographic_economic_plot <- all_demographic_economic %>%
  plot_ly(
    x = ~ Survey,
    y = ~ lower_income,
    type = "bar",
    name = "Lower Income"
  )
all_demographic_economic_plot <-  all_demographic_economic_plot %>%
  add_trace(y = ~ middle_income, name = "Middle Income") %>%
  add_trace(y = ~ high_income, name = "High Income")

all_demographic_economic_plot <-
  all_demographic_economic_plot %>% layout(
    xaxis = list(categoryorder = "trace"
                 ),
    yaxis = list(title = "Percent"), 
    barmode = "stack",
    title = "Economic Target Population",
         colorway=duke_colorway,
         paper_bgcolor = duke_paperbackground,
    plot_bgcolor = duke_plotcolor,
     margin = m,
    font=plot_font
     )

all_demographic_economic_plot
```




### Geographic Information

Target groups were also differentiated by location: Urban, suburban/periurban, and rural.

```{r geographic_information}
baseline_geographic_demo <- baseline_data %>%
                          select(Survey:Organization, urban:rural) %>% 
                            mutate(across(urban:rural,as.integer))

midline_geographic_demo <- midline_data %>% 
                            select(Survey:Organization, urban:rural) %>% 
                            mutate(across(urban:rural,as.integer))

endline_geographic_demo <- endline_data %>% 
                            select(Survey:Organization, urban:rural) %>% 
                             mutate(across(urban:rural,as.integer))

all_geographic_demo <- baseline_geographic_demo %>% 
                      bind_rows(midline_geographic_demo) %>% 
                      bind_rows(endline_geographic_demo)

all_geographic_demo_table <- all_geographic_demo %>% 
                        group_by(Survey) %>% 
                        summarise(urban = mean(urban), suburban_periurban = mean(suburban_periurban), rural = mean(rural))

```


```{r plot_geographic}

all_geographic_demo_plot <- all_geographic_demo_table %>%
  plot_ly(
    x = ~ Survey,
    y = ~ rural,
    type = "bar",
    name = "Rural"
  )
all_geographic_demo_plot <-  all_geographic_demo_plot %>%
  add_trace(y = ~ suburban_periurban, name = "Suburban/Peri-Urban") %>%
  add_trace(y = ~ urban, name = "Urban")

all_geographic_demo_plot <-
all_geographic_demo_plot %>% layout(
    xaxis = list(categoryorder = "array",
                 categoryarray = c("baseline", "midline", "endline")),
    yaxis = list(title = "Percent"), 
    barmode = "stack",
  title = "Geographic Target Population",
         colorway=duke_colorway,
         paper_bgcolor = duke_paperbackground,
    plot_bgcolor = duke_plotcolor,
     margin = m,
    font=plot_font
     )

all_geographic_demo_plot

```

### Geographic trends

The focus becomes more urban over time.


## Human Resources Trends

Organizations provided information on their hiring practices over the course of the fellowship. Particular attention was paid to gender distribution.

```{r gender}

baseline_hr_gender <- baseline_data %>%
  select(Survey:Organization, full_time_total:part_time_female) %>%
  mutate(across(full_time_total:part_time_female, as.integer))

midline_hr_gender <- midline_data %>%
  select(Survey:Organization, full_time_total:part_time_female) %>%
  mutate(across(full_time_total:part_time_female, as.integer))

endline_hr_gender <- endline_data %>%
  select(Survey:Organization, full_time_total:part_time_female) %>%
  mutate(across(full_time_total:part_time_female, as.integer))

```

```{r gender_percent}

full_hr_gender <- baseline_hr_gender %>%
  left_join(midline_hr_gender,
            by = "OrgID",
            suffix = c("_baseline", "_midline")) %>%
  left_join(endline_hr_gender,
            by = "OrgID",
            suffix = c("_baseline", "_endline")) %>%
  select(!(Organization_midline)) %>%
  select(!(Organization)) 
  

prct_changes_ft_all <- full_hr_gender %>%
  mutate(
    baseline = 0,
    midline = (full_time_total_midline -
                  full_time_total_baseline) / full_time_total_baseline,
    
    endline = (full_time_total - full_time_total_midline)/ full_time_total_midline) %>% 
  select(!(full_time_total_baseline:part_time_female)) %>% 
  select(!(1)) %>% 
  mutate(across(everything(), ~replace_na(.,0))) %>% 
  bind_rows(summarise(., OrgID = 0,
                      across(baseline:endline, mean),
                      across(where(is.character), ~"Mean"))) %>% 
  pivot_longer(baseline:endline, names_to = "survey", values_to = "full_time_total")  
  
prct_changes_ft_f <- full_hr_gender %>%
  mutate(
    baseline = 0,
    midline = (full_time_female_midline -
                  full_time_female_baseline) / full_time_female_baseline,
    
    endline = (full_time_female - full_time_female_midline)/ full_time_female_midline) %>% 
  select(!(full_time_total_baseline:part_time_female)) %>% 
  select(!(1)) %>% 
  mutate(across(everything(), ~replace_na(.,0))) %>% 
  bind_rows(summarise(., OrgID = 0,
                      across(baseline:endline, mean),
                      across(where(is.character), ~"Mean"))) %>% 
  pivot_longer(baseline:endline, names_to = "survey", values_to = "full_time_female") 

prct_changes_pt_all <- full_hr_gender %>%
  mutate(baseline =0,
    midline = ifelse(
      part_time_total_baseline != 0, (part_time_total_midline -
         part_time_total_baseline) / part_time_total_baseline,0),
    
    endline = ifelse(
      part_time_total_baseline != 0,
      (part_time_total -
         part_time_total_midline)
      / part_time_total_midline,
      0
    )
  )%>% 
  select(!(full_time_total_baseline:part_time_female)) %>% 
  select(!(1)) %>% 
  mutate(across(everything(), ~replace_na(.,0))) %>% 
  bind_rows(summarise(., OrgID = 0,
                      across(baseline:endline, mean),
                      across(where(is.character), ~"Mean"))) %>% 
  pivot_longer(baseline:endline, names_to = "survey", values_to = "part_time_total") 

prct_changes_pt_female <- full_hr_gender %>%
  mutate(baseline = 0,
    midline = ifelse(
      part_time_female_baseline != 0,
      (part_time_female_midline -
         part_time_female_baseline) / part_time_female_baseline,
      0
    ),
    
    endline = ifelse(
      part_time_female_midline != 0,
      (part_time_female -
         part_time_female_midline)
      / part_time_female_midline,
      0
    )
  )%>% 
  select(!(full_time_total_baseline:part_time_female)) %>% 
  select(!(1)) %>% 
  mutate(across(everything(), ~replace_na(.,0))) %>% 
  bind_rows(summarise(., OrgID = 0,
                      across(baseline:endline, mean),
                      across(where(is.character), ~"Mean"))) %>% 
  pivot_longer(baseline:endline, names_to = "survey", values_to = "part_time_female") 


```

```{r recombine_data}

all_percent_change <- prct_changes_ft_all %>% 
                      left_join(prct_changes_ft_f, by = c("OrgID"="OrgID", "Organization_baseline" = "Organization_baseline", "survey" = "survey")) %>% 
                      left_join(prct_changes_pt_all, by = c("OrgID"="OrgID", "Organization_baseline" = "Organization_baseline", "survey" = "survey")) %>% 
                      left_join(prct_changes_pt_female, by = c("OrgID"="OrgID", "Organization_baseline" = "Organization_baseline", "survey" = "survey")) %>% 
                      rename(Organization = Organization_baseline) %>% 
                      pivot_wider(Organization:survey, names_from = Organization, values_from = full_time_total:part_time_female) %>% 
                      add_column(dummy_total = 0) %>% 
                      add_column(dummy_women = 0) %>% 
                      add_column(date= c("2020-11-01","2021-05-01","2021-12-01")) %>% 
                      mutate(date = as_date(date))

```

```{r plot_full_time_all}

plot_full_time_all <- all_percent_change %>%
  plot_ly(
    x = ~ date,
    y = ~ `full_time_total_Lily Health`,
    type = 'scatter',
    mode = 'lines',
    name = "Lily Health",
    line = list(color = duke_colorway [1],width = 1),
    opacity = .4,
     legendrank = 6
  ) %>%
  add_trace(
    y =  ~ `full_time_female_Lily Health`,
    name = "Lily Health (Women)",
    line = list(color = duke_colorway[1], dash = "dash"),
    showlegend = FALSE

  ) %>%
  add_trace(
    y =  ~ `full_time_total_Kasole Secrets Company Ltd`,
    name = "Kasole Secrets Company",
    line = list (color = duke_colorway[2]),
     legendrank = 5
    
  ) %>%
  add_trace(
    y =  ~ `full_time_female_Kasole Secrets Company Ltd`,
    name = "Kasole Secrets Company (Women)",
    line = list (color = duke_colorway[2], dash = 'dash'),
    showlegend = FALSE
  ) %>%                     
  add_trace(
    y =  ~ `full_time_total_Femme International`,
    name = "Femme International",
    line = list (color = duke_colorway[3]),
     legendrank = 4
    
  ) %>% 
add_trace(
    y =  ~ `full_time_female_Femme International`,
    name = "Femme International (Women)",
    line = list (color = duke_colorway[3], dash = "dash"),
    showlegend = FALSE
    
  ) %>% 

  add_trace(
    y =  ~ `full_time_total_SaCoDé`,
    name = "SaCoDé",
    line = list (color = duke_colorway[4]),
     legendrank = 8
  ) %>%
  add_trace(
    y =  ~ `full_time_female_SaCoDé`,
    name = "SaCoDe (Women)",
    line = list (color = duke_colorway[4], dash = "dash"),
    showlegend = FALSE
  ) %>%
  add_trace(
    y =  ~ `full_time_total_Tai Tanzania`,
    name = "Tai Tanzania",
    line = list (color = duke_colorway[5]),
     legendrank = 9
    
  ) %>%
  add_trace(
    y =  ~ `full_time_total_Tai Tanzania`,
    name = "Tai Tanzania (Women)",
    line = list (color = duke_colorway[5], dash = "dash"),
    showlegend = FALSE
    
  ) %>%
  add_trace(
    y =  ~ `full_time_total_LVCT HEALTH`,
    name = "LVCT Health",
    line = list (color = duke_colorway[6]),
     legendrank = 7
  ) %>%
  add_trace(
    y =  ~ `full_time_female_LVCT HEALTH`,
    name = "LVCT Health (Women)",
    line = list (color = duke_colorway[6], dash = "dash"),
    showlegend = FALSE
  ) %>%
  add_trace(
    y =  ~ `full_time_total_Mean`,
    name = "Mean",
    line = list (color = duke_colorway[7], width = 2),
    legendrank = 3,
    opacity = 1
  ) %>%
  add_trace(
    y =  ~ `full_time_female_Mean`,
    name = "Mean (Women)",
    line = list (
      color = duke_colorway[7],
      width = 2,
      dash = "dash"),
      showlegend= FALSE,
    opacity = 1
    
    
  ) %>%
  add_trace(
    y = ~ dummy_total,
    name = "All Full-Time",
    line = list(color = "rgb(0,0,0)"),
    #visible = "legendonly",
    showlegend = TRUE,
    legendrank = 1
   
  ) %>%
  add_trace(
    y = ~ dummy_women,
    name = "Full-Time Women",
    line = list(color = "#000000", dash = "dash"),
    legendrank = 2
    
    )

plot_full_time_all <- plot_full_time_all %>%
  layout(
    xaxis = list(
     # categoryorder = "array",
    type = "date",
    tickmode = "array",
    tickvals = c("2020-11-01","2021-05-01","2021-12-01"),
    tickformat = "%Y-%b",
    #rangebreaks = list(values = c("2020-11-01","2021-05-01","2021-12-01")),
      showgrid = FALSE
    ),
    yaxis = list(title = "Percent Change", showgrid = FALSE, tickformat = ".0%"),
    title = "Full Time Employment Change",
    
    paper_bgcolor = duke_paperbackground,
    plot_bgcolor = duke_plotcolor,
    margin = m,
    font = plot_font
  )

plot_full_time_all
```

In general, the employment data shows a downward trend. On average organizations reduced their workforce by `r round(all_percent_change$full_time_total_Mean[3]*100,0)`%, with the female workforce reducing by an equal amount `r round(all_percent_change$full_time_female_Mean[3]*100,0)`%. 

## Revenue
They made money

```{r revenue_table}
revenue <- endline_data %>% 
            select (c(2:3, revenue_2019:revenue_2021)) %>% 
            mutate(across(revenue_2019:revenue_2021, as.numeric)) %>% 
            mutate(Mean = rowMeans(across(revenue_2019:revenue_2021),na.rm = TRUE))  %>% 
            arrange(Organization) %>% 
            mutate(OrgOrder = row_number())

            #pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
            #mutate(Year = str_remove_all(Year, "revenue_")) %>% 
            #pivot_wider(Year,names_from = Organization, values_from = Revenue)
```


```{r individual_revenue_tables}
#Generate individual tables

revenue_1 <- revenue %>% 
             filter(OrgOrder ==1) %>% 
             pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
             mutate(Year = str_remove_all(Year, "revenue_")) 

revenue_2 <- revenue %>% 
             filter(OrgOrder ==2) %>% 
             pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
             mutate(Year = str_remove_all(Year, "revenue_")) 

revenue_3 <- revenue %>% 
             filter(OrgOrder ==3) %>% 
             pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
             mutate(Year = str_remove_all(Year, "revenue_"))

revenue_4 <- revenue %>% 
             filter(OrgOrder ==4) %>% 
             pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
             mutate(Year = str_remove_all(Year, "revenue_")) 

revenue_5 <- revenue %>% 
             filter(OrgOrder ==5) %>% 
             pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
             mutate(Year = str_remove_all(Year, "revenue_")) 

revenue_6 <- revenue %>% 
             filter(OrgOrder ==6) %>% 
             pivot_longer(revenue_2019:Mean, names_to = "Year", values_to = "Revenue") %>% 
             mutate(Year = str_remove_all(Year, "revenue_")) 
```

```{r revenue_plot}

plot_revenue_1 <- revenue_1 %>% 
                plot_ly(
                  x = ~Year,
                  y = ~Revenue,
                  type = "bar",
                  marker = list(color = duke_colorway[1:4])
                )  %>% 
  layout(yaxis = list(tickprefix = "$"))
                

plot_revenue_2 <- revenue_2 %>% 
                plot_ly(
                  x = ~Year,
                  y = ~Revenue,
                  type = "bar",
                  marker = list(color = duke_colorway[1:4])
                ) %>% 
  layout(yaxis = list(tickprefix = "$"))
               

plot_revenue_3 <- revenue_3 %>% 
                plot_ly(
                  x = ~Year,
                  y = ~Revenue,
                  type = "bar",
                  marker = list(color = duke_colorway[1:4])
                ) %>% 
  layout(yaxis = list(tickprefix = "$"))
              

plot_revenue_4 <- revenue_4 %>% 
                plot_ly(
                  x = ~Year,
                  y = ~Revenue,
                  type = "bar",
                  marker = list(color = duke_colorway[1:4])
                ) %>% 
  layout(yaxis = list(tickprefix = "$"))
               

plot_revenue_5 <- revenue_5 %>% 
                plot_ly(
                  x = ~Year,
                  y = ~Revenue,
                  type = "bar",
                  marker = list(color = duke_colorway[1:4])
                ) %>% 
  layout(yaxis = list(tickprefix = "$"))
               
plot_revenue_6 <- revenue_6 %>% 
                plot_ly(
                  x = ~Year,
                  y = ~Revenue,
                  type = "bar",
                  marker = list(color = duke_colorway[1:4])
                ) %>% 
  layout(yaxis = list(tickprefix = "$"))
                

plot_revenues <- subplot(plot_revenue_1, plot_revenue_2, plot_revenue_3,plot_revenue_4,plot_revenue_5,plot_revenue_6, nrows = 3, shareX = TRUE, margin=.05) %>% 
  layout(title = list(text = "Yearly Revenue by Organization"),
                  yaxis = list(tickprefix = "$"),
                  paper_bgcolor = duke_paperbackground,
                  plot_bgcolor = duke_plotcolor,
                  margin =list(t=50),
                  font = list(
  family = "'Playfair Display','Helvetica Neue',Helvetica,Arial,sans-serif",
  size = 12,
  color = '#363636'),
                           showlegend=FALSE
                  )


annotations = list( 
  list( 
    x = 0.2,  
    y = 1.0,  
    text = revenue_1$Organization[1],  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.8,  
    y = 1,  
    text = revenue_2$Organization[1],  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),  
  list( 
    x = 0.2,  
    y = 0.625,  
    text = revenue_3$Organization[1],  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),
  list( 
    x = 0.8,  
    y = 0.625,  
    text = revenue_4$Organization[1],  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),
  list( 
    x = 0.825,  
    y = 0.45,  
    text = "2021 data<br>pending",  
    xref = "paper",  
    yref = "paper",  
    align = "left",
    
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),
  list( 
    x = 0.2,  
    y = 0.3,  
    text = revenue_5$Organization[1],  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  ),
  list( 
    x = 0.8,  
    y = 0.3,  
    text = revenue_6$Organization[1],  
    xref = "paper",  
    yref = "paper",  
    xanchor = "center",  
    yanchor = "bottom",  
    showarrow = FALSE 
  )
  
  )

plot_revenues <- plot_revenues %>% layout(annotations=annotations)


plot_revenues







```





```{r}
sum_unique <- endline_data %>% 
              summarise(sum(as.double(unique_served)))

```

